Analysis of split plot design using MCMCglmm

### 2018-04-14 README.Rmd
Update README

The files at the URL above will generate the results as found in the
publication. The files hosted at github.com/openplantpathology/rice.awd.pests
are the development versions and may have changed since the report was
published.

@@

@@

- the manuscript as submitted (in PDF format) and it's Rmd source file
- all the data files (in CSV file format, in the `data/` directory)
- supplementary information source files (in R markdown format) and executed versions
- all the figures that are included in the paper (in the `figures/` directory)

@@

This repository is organized as an R package. There are no actual R functions in
this package - all the R code is in the Rmd file. I simply used the R package
structure to help manage dependencies, to take advantage of continuous
integration for automated code testing, and so I didn't have to think too much
about how to organise the files.

@@

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these
can be time-consuming and complicated, so we've done two things to simpify
access to the compendium. First is the packrat directory, which contains the
source code for all the packages we depend on. If all works well, these will be
installed on your computer when you open `rice_awd_.pests.Rproj` in RStudio.
Second is our Docker image that includes all the necessary software, code and
data to run our analysis. The Docker image may give a quicker entry point to the
project, and is more self-contained, so might save some fiddling with installing
things.

@@

Once logged in, use the Files pane (bottom right) to navigate to `/` (the root
directory), then open the folder for this project, and open the `.Rproj` file
for this project. Once that's open, you'll see the `analysis/paper` directory in
the Files pane where you can find the R markdown document, and knit them to
produce the results in the paper. More information about using RStudio in Docker
is avaiable at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

We developed and tested the package on this Docker container, so this is the
only platform that We're confident it works on, and so recommend to anyone
wanting to use this package to generate the vignette, etc.

@@

>>>>

The files at the URL above will generate the results as found in the
publication. The files hosted at
<https://github.com/openplantpathology/rice_awd_pests> are the development
versions and may have changed since the report was published.

@@

The `data-raw` directory contains:

- a Rmd file and Markdown file detailing how the raw data was handled and
Area Under the Disease Progress Stairs (AUDPS) was calculated for analysis and
the .Rda files used in the analysis were generated

@@

- the manuscript as submitted (in MS Word format) and it's Rmd source file

- all the data files (in CSV file format, in the `data/` directory)

- supplementary information source files (in R markdown format) and executed
versions

- all the figures that are included in the paper (in the `figures/` directory)

@@

This repository is organized as an R package. There are a few R functions in
this package that were used to generate some of the diagnostic plots related to
the analysis. However, for the most part I simply used the R package
structure to help manage dependencies, to take advantage of continuous
integration for automated code testing, and so I didn't have to think too much
about how to organise the files.

@@

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these
can be time-consuming and complicated, so we've used a Docker image. The Docker
image includes all the necessary software, code and data to run our analysis.
The Docker image may give a quicker entry point to the project, and is more
self-contained, so might save some fiddling with installing things.

@@

Once logged in, use the Files pane (bottom right) open the folder for this
project, and open the `.Rproj` file for this project. Once that's open, you'll
see the `analysis/paper` directory in the Files pane where you can find the R
markdown document, and knit them to produce the results in the paper. More
information about using RStudio in Docker is avaiable at the
[Rocker](https://github.com/rocker-org)
[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

We developed and tested the package on this Docker container, so this is the
only platform that we're confident it works on, and so recommend to anyone
wanting to use this package to generate the vignettes, etc.

@@

## Required packages
 - agricolae
 - bookdown
 - car
 - carData
 - dplyr (>= 0.7.0)
 - fitdistrplus
 - forcats
 - ggplot2
 - ggpubr
 - kableExtra
 - knitr
 - lattice
 - lubridate
 - MASS
 - MCMCglmm
 - reshape2
 - rmarkdown
 - plotMCMC
 - purrr (>= 0.2.3)
 - tibble
 - tidyr (>= 0.7.0)
